% This document has flags available which will affect the compilation and resulting file.
% The idea for using flags is taken from: https://tex.stackexchange.com/a/19077/73813
% The idea for using conditionals is taken from: https://tex.stackexchange.com/a/5896/73813
%
% To compile this resume with all content use "pdflatex master_list.tex"
% To compile this resume with some of the content use:
%   "pdflatex '\def\resumetype{<value>}\input{master_list.tex}'"
% E.g.
%   "pdflatex '\def\resumetype{0}\input{master_list.tex}'"
%
% Valid values are:
%   0 - For a software oriented resume
%
%

\documentclass[a4paper]{article}
\usepackage{etoolbox}  % For convenient handling of conditionals.

\newtoggle{software}
\newtoggle{hardwareswe}
\newtoggle{electrical}
\newtoggle{portfolio}
\newtoggle{olderinternships}
\newtoggle{preuni}
\newtoggle{allprojects}
\newtoggle{evaluations}

\toggletrue{software}
\toggletrue{hardwareswe}
\toggletrue{electrical}
\toggletrue{portfolio}
\toggletrue{olderinternships}
\toggletrue{preuni}
\toggletrue{allprojects}
\toggletrue{evaluations}

% Handle flags. All defaults to true.
\ifdefined\resumetype
% Case 0 - software
\ifcase\resumetype\relax
  \toggletrue{software}
  \togglefalse{hardwareswe}
  \togglefalse{electrical}
  \togglefalse{olderinternships}
  \togglefalse{portfolio}
  \togglefalse{preuni}
  \togglefalse{allprojects}
  \togglefalse{evaluations}
  % \or
  % Case 1 - hardware swe
  \else
  \toggletrue{software}
  \toggletrue{hardwareswe}
  \togglefalse{electrical}
  \togglefalse{olderinternships}
  \togglefalse{portfolio}
  \togglefalse{preuni}
  \togglefalse{allprojects}
  \togglefalse{evaluations}
  % Nothing. But it shouldn't get here unless the wrong value was used.
  \fi
\else
  % No flag provided. Leave defaults (all flags true).
\fi


\usepackage[T1]{fontenc}
\usepackage{titlesec}  % \section
\usepackage{anyfontsize}  % \fontsize
\usepackage[dvipsnames]{xcolor}  % \definecolor
\usepackage{enumitem}  % For resume bullet items.
\usepackage{multirow}  % \multirow - for heading.

\usepackage{librebaskerville}  % Use \librebaskerville to set font family
\renewcommand{\familydefault}{\sfdefault}  % Set default back to standard


\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage[empty]{fullpage}  % Affects page alignment

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\fontfamily{cmr}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% --------------------------
% ---------- Custom Commands

% Colors
\definecolor{tealblue}{RGB}{31, 78, 121}
\definecolor{slightgray}{gray}{0.5}
\definecolor{lightergray}{gray}{0.4}

% Heading title.
\newcommand{\nametitle}[2]{%
\librebaskerville%
\fontseries{b}%
\fontsize{45}{54}%
\selectfont%
#1 \textcolor{tealblue}{#2}
}

% HeaderSpacing. {left_aligned}{right_aligned}
\newcommand{\headeralgined}[2]{%
\normalfont%
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}%
  #1 & #2 \\%
\end{tabular*}%
\vspace{-6pt}%
}

% Education heading. {Degree}{University}{Years}
\newcommand{\education}[3]{%
  \headeralgined{%
    #1,~\textit{#2}%
  }{#3}
}


% Experience heading. {Role}{Company}{Dates}
\newcommand{\experience}[3]{%
  \headeralgined{%
    \textbf{#1},~\textit{#2}%
  }{#3}%
  \vspace{1pt}
}

% Project heading. {Name}{Technologies}{Dates}
\newcommand{\project}[3]{%
  \headeralgined{%
    #1~\textemdash~#2%
  }{#3}
}

% Performance Evaluation. {Quote}{Name}{Role}{Company}
\newcommand{\evaluation}[4]{%
  \textcolor{lightergray}{\textit{"#1"}}%
  \newline%
  - #2, #3, \textit{#4}%
  \vspace{5pt}
}

% Items under a heading.
\newcommand{\resumeitemstartlist}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeitemendlist}{\end{itemize}\vspace{2pt}}
\newcommand{\resumeitem}[1]{%
  \item{\normalsize{#1\vspace{-4pt}}}%
}

\newcommand{\tech}[1]{%
\textcolor{tealblue}{#1}%
}

% -----------------------------------------
% ---------- End Custom Commands ----------

\begin{document}

{  % Name and contact info
\begin{flushleft}  % For aligning table left
  \iftoggle{portfolio}{%
    \renewcommand{\arraystretch}{1.1}  % Increase row separation
  }{}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \iftoggle{portfolio}{%
      \multirow{3}{*}{\nametitle{Chris}{Gravel}}%
    }{%
      \multirow{2}{*}{\nametitle{Chris}{Gravel}}%
    }
    &
    \iftoggle{portfolio}{}{%
      \vspace{5pt}  % Add vertical space only if portfolio is not printed.
    }
    \textcolor{slightgray}{%
      chrisgravel@live.com
    } \\
    &
    \textcolor{slightgray}{%
      linkedin.com/in/cpagravel
    } \\
    \iftoggle{portfolio}{%
      &
      \textcolor{slightgray}{%
        chrisgravel.wixsite.com/portfolio
      } \\
    }{}
  \end{tabular*}
\end{flushleft}
\vspace{8pt}
}

% ---------- Education

\section{Education}
\education{BASc Mechatronics Engineering with AI Option}{University of Waterloo}{2014 - 2019}

% ---------- Skills

\section{Skills}
\begin{tabular*}{\textwidth}{l@{\hskip 0.2in}l}%
  Software Languages
  &
  Python,
  C,
  C++,
  Bash,
  SQL,
  Matlab,
  Javascript
  \\

  Software Tools
  &
  Microcontrollers,
  Linux,
  ROS,
  Git,
  OpenCV
  \iftoggle{electrical}{\vspace{5pt}}{}  % Add space to separate electrical.
  \\

  \iftoggle{electrical}{%
    Electrical Concepts
    &
    Motor Controllers,
    Schematic Capture,
    PCB Layout,
    Power Supplies,
    FPGA Design
    \\

    Electrical Tools
    &
    Oscilloscope,
    DMM,
    LCR Meter,
    Soldering Iron,
    Signal Generator,
    Eagle PCB Software
    \\
  }{}

\end{tabular*}%

% ---------- Experience

\section{Experience}


\experience{Senior Software Engineer (Nest)}{Google LLC}{Sept 2019 - Present}
\resumeitemstartlist
{%
  \resumeitem{%
    Led a team of 5 engineers to design and build infrastructure for supporting Google's Matter launch.
    The infra we built supports creating dynamic topologies of real devices with a complex configuration
    matrix of more than 100 params and served as a release gate for millions of devices.
    \tech{(Python)}
  }
  \resumeitem{%
    Designed and implemented pipelines for continuous delivery and continuous integration testing.
    Integrated pipelines across multiple ecosystems (Google internal, Github, Gerrit, Jenkins).
    \tech{(Python, Bash, Docker, Jenkins)}
  }
  \resumeitem{%
    Scoped infrastructure work for supporting new hardware in our test automation.
    Took ownership of design, and implementation while leading and providing guidance for junior SWEs.
    Infrastructure supported 20+ hardware devices, 1000+ automation tests, and impacts millions of users.
    \tech{(Python)}
  }
  \resumeitem{%
    Ideated and implemented a novel solution that applies statistical tools for detecting software
    regressions involving latency which reduced engineering effort to root cause from 4 hours to 1 min.
    \tech{(Python, SQL, Jenkins, Two sample T-test, DataStudio)}
  }
  \resumeitem{%
    Used optimization and ML techniques to create a flicker detection algorithm with a 96\% recall rate.
    \tech{(Python, numpy, scipy, skimage)}
  }
  \resumeitem{%
    Mentored engineers to help them advance in their career and adapt to the professional environment.
    Arranged quarterly team gatherings for 15+ people.
    Took advice from those willing to teach me.
    \tech{(Soft skills)}
  }
}
\resumeitemendlist


\experience{Perception Team Engineer}{Avidbots Corp.}{May 2018 - Aug 2018}
\resumeitemstartlist
{%
  \resumeitem{%
    Developed mathematical model for optimal sensor layout for cliff detection using 1D sensors.
    \tech{(Python, Geometry, Numerical Methods)}
  }
  \resumeitem{%
    Automated collection and labelling of vision data using localization information and camera feeds on the robot.
    \tech{(OpenCV, Python, C++)}
  }
}
\resumeitemendlist


\experience{IoT \& AI Developer}{IBM}{Sept 2017 - Dec 2017}
\resumeitemstartlist
{%
  \resumeitem{%
    Created real-time object recognition solution with 95\% accuracy for POC contract using
    supervised learning on a FasterRCNN network.
    \tech{(Python, FasterRCNN)}
  }
}
\resumeitemendlist


\experience{Robotics Software Developer}{Avidbots Corp.}{Jan 2017 - April 2017}
\resumeitemstartlist
{%
  \resumeitem{%
    Developed numerical model in C++ and Matlab for simulating trajectory to determine traversal time.
    \tech{(C++, Python, ROS, Matlab, Numerical Methods)}
  }
  \resumeitem{%
    Improved performance by 10\% by minimizing kinematic accelerations on robot caused by trajectory jaggedness.
    \tech{(C++, ROS, OpenCV)}
  }
  \resumeitem{%
    Wrote unit tests for a robotics system on the ROS platform in C++ using the Google test framework.
    \tech{(C++, ROS)}
  }
}
\resumeitemendlist

\ifboolexpr{ togl {electrical} or togl {hardwareswe} }{%
  \experience{Junior Hardware Designer}{Imagine Communications}{May 2016 - Aug 2016}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Wrote VHDL code to optimize FPGA implementation of an Ethernet receiver which reduced read clock cycles by 8x.
      \tech{(VHDL)}
    }
    \resumeitem{%
      Designed and implemented a FPGA component which captures and records ethernet packets for debugging.
      \tech{(VHDL)}
    }
    \resumeitem{%
      Automated hardware testing using electrical instrumentation and Python APIs.
      \tech{(Python)}
    }
  }
  \resumeitemendlist


  \experience{Mechatronics Prototyper}{Engineering Ideas Clinic}{Sept 2015 - Dec 2015}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Created schematics, layouts, and soldered PCBs to create proof of concept prototypes
    }
    \resumeitem{%
      Salvaged parts from E-waste bins for use in prototypes to save over \$1,000 in resources
    }
    \resumeitem{%
      Designed and built an AM Radio to be used as a teaching aid for 4th year electrical students.
    }
  }
  \resumeitemendlist


  \experience{Web App Developer}{Computer Science Computing Facility}{Jan 2015 - April 2015}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Improved performance of a core web app by 2,000\%, reducing page load time by 13 seconds.
    }
    \resumeitem{%
      Indexed database by cardinality to improve lookup time in relational database.
    }
  }
  \resumeitemendlist
}{}

\iftoggle{preuni}{%
  \experience{Roughneck}{Nabors Drilling Ltd.}{Jan 2013 - Dec 2013}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Applied mechanical knowledge to fix and maintain industrial pumps and hydraulic motors.
    }
    \resumeitem{%
      Assisted mechanic with routine repairs to large megawatt diesel generator.
    }
  }
  \resumeitemendlist


  \experience{Infantryman}{Canadian Military}{Jan 2004 - Dec 2009}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Exercised discipline and teamwork to perform coordinated large scale military operations in Afghanistan.
    }
    \resumeitem{%
      Adapted to harsh environments and working conditions to achieve mission objectives.
    }
  }
  \resumeitemendlist
}{}

% ---------- Engineering Projects

\section{Engineering Projects}
\ifboolexpr{ togl {software} or togl {allprojects} }{%
  \project{Optimization of Vehicle Suspension using Enhanced Hillclimbing}{Python, Matlab}{2018}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Created a novel search algorithm that outperforms other state-of-the-art search algorithms in the field.
    }
  }
  \resumeitemendlist
}{}


\ifboolexpr{ togl {electrical} or togl {allprojects} }{%
  \project{Autonomous Submarine Robot}{Python, Bash, OpenCV, Electrical CAD}{2018}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Designed an autonomous submarine that navigates an obstacle course.
    }
    \resumeitem{%
      Designed software system to optimize for I/O sensor readings and maximize resource utilization.
    }
    \resumeitem{%
      Implemented localization using OpenCV on webcam feed to find prominent features in the environment.
    }
  }
  \resumeitemendlist
}{}


% \iftoggle{software}{%
\ifboolexpr{ togl {software} or togl {allprojects} }{%
  \project{Git Status Tool (gst)}{Python}{2018}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Commandline tool for improving my own Git workflow. Compatible with Mac and Linux.
    }
  }
  \resumeitemendlist
}{}


\ifboolexpr{ togl {software} or togl {allprojects} }{%
  \project{Asteroids Game built on ARM Cortex-M microcontroller}{C}{2016}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Re-created the game of Asteroids on an ARM Cortex-M microcontroller with RTOS.
    }
    \resumeitem{%
      Used semaphores and mutexes to enable synchronous multitasking operations.
    }
    \resumeitem{%
      Created physics engine to model the original game physics.
    }
  }
  \resumeitemendlist
}{}


\iftoggle{allprojects}{%
  \project{Line Following Robot}{C}{2016}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Constructed circuitry for filtering signals from hall effect sensors and photodiodes.
    }
    \resumeitem{%
      Programmed PIC microcontroller with logic necessary to follow line.
    }
    \resumeitem{%
      Debugged hardware and software problems.
    }
  }
  \resumeitemendlist
}


\iftoggle{allprojects}{%
  \project{Real-Time Memory Management using Half-Fit Algorithm}{C}{2016}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Implemented the half-fit memory managing algorithm designed for a real-time system.
    }
  }
  \resumeitemendlist
}


\ifboolexpr{ togl {electrical} or togl {allprojects} }{%
  \project{Linear Variable Differential Transformer}{Schematic Capture, Breadboarding, Oscilloscope}{2016}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Created a measuring sensor with a precision of 0.1 mm using magnetic coupling between transformers.
    }
    \resumeitem{%
      Used an isolation transformer to prevent the change in load from affecting the measurement.
    }
  }
  \resumeitemendlist
}


\ifboolexpr{ togl {electrical} or togl {allprojects} }{%
  \project{Amplitude Modulated Long Wave Radio Receiver}{Schematic Capture, PCB Design, Oscilloscope}{2015}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Tuned resonant frequency of tank circuit to receive signals in the range of 400-800 kHz with high Q.
    }
    \resumeitem{%
      Biased BJT transistor to amplify incoming signal from 0.2V to 2V to overcome voltage drop in envelope detector.
    }
  }
  \resumeitemendlist
}


\ifboolexpr{ togl {electrical} or togl {allprojects} }{%
  \project{High Speed Pickup Winder With LCD Interface}{Schematic Capture, Arduino}{2015}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Designed uni-polar motor controller circuit with heat sink and pulse width modulated power control.
    }
    \resumeitem{%
      Used Arduino timer interrupts to achieve a rate of 3500 rpm, winding a pickup in 10 minutes—54x faster than prior design.
    }
  }
  \resumeitemendlist
}


\iftoggle{allprojects}{%
  \project{Medical Compactable Ergonomic Chair}{CAD}{2015}
  \resumeitemstartlist
  {%
    \resumeitem{%
      Donated over 200 hours to design and build a special chair for a man with debilitating nerve pain.
    }
  }
  \resumeitemendlist
}

% ---------- Achievements

\section{Achievements}
\resumeitemstartlist
{%
  \resumeitem{%
    Runner-up in an international IBM internal coding competition (CodeBlue 2017).
  }
  \resumeitem{%
    Received multiple awards (1 Google Tech Impact Award, 1 DSPA Tech Award, 5 spot bonuses, 8 peer bonuses) at Google due to contributions.
  }
  \resumeitem{%
    Received Python readability status at Google which allows me to approve Python changes for their style.
  }
  \iftoggle{preuni}{%
    \resumeitem{%
      Campaign Medal from serving in Afghanistan in 2008 with the Canadian Military.
    }
    \resumeitem{%
      Hosted a tour and travel TV show in Indonesia with over 1,000,000 viewers.
    }
  }{}
}
\resumeitemendlist

% ---------- Performance Evaluations
\pagebreak
\iftoggle{evaluations}{%
  \begin{samepage}

    \section{Internship Evaluations}
    \vspace{5pt}
    \evaluation{%
      Chris performed beyond all our expectations and was instrumental in completing critical tasks
      for a client project. We were able to depend on him to complete his work in a timely manner with
      high quality and he was enthusiastic in his desire to learn and contribute to the team.
      Excellent work!%
    }{Asim Raoof}{Senior Application Developer}{IBM}

    \evaluation{%
      Superbly well-rounded, was able to keep up with and surpass the performance of veteran full-time
      employees on the team. He made many sound and informative suggestions, led and executed on ideas
      he resourcefully managed, and thoroughly educated the team on the rationale of all decisions.
      His technical capabilities and understanding of start-up business challenges help inform his
      conduct on all tasks. He was always passionate and intrigued by all aspects of work.
      He was capable of working autonomously with minimal supervision.%
    }{Kenneth Lee}{Coverage Planning Team Lead}{Avidbots}

    \evaluation{%
      Chris' efforts throughout the term contributed greatly to the success of the both new, and
      existing, activities this semester. By the end of the term, the team of clinic co-ops were
      functioning as a well-oiled machine, rotating in and out of tasks as needed with minimal
      supervision. With very little supervision, when Chris had a question that needed answering,
      he tracked down the correct person to answer it. The quality of his work was exemplary throughout
      the term, with the guitar pickup winder being a notable example. Chris' enthusiasm for the work,
      and for learning, carried him through the term. Chris has a bright future ahead if he can just
      slow and enjoy the sights a little.%
    }{Chris Rennick}{Engineering Educational Developer}{Engineering Ideas Clinic}

    \evaluation{%
      Christopher worked with us to develop lab equipment for engineering education. He was given a
      very challenging project and there was little direction from his supervisors. He was able to get
      the project finished to a degree that was beyond anyone's expectations. Furthermore,
      Christopher's work ethic was impeccable. He routinely sought out contacts and resources to help
      him get the job done, and was always there when needed for urgent projects.%
    }{Mike Stachowski}{Engineering Educational Developer}{Engineering Ideas Clinic}

    \evaluation{%
      Christopher was all around an ideal employee, and a great fit for our group. He came in with good
      web developer habits, fit in with our group quite well, set the bar extremely high for his own work,
      and delivered more than what was asked- sometimes much more, within the amount of time we had budgeted.
      He left us having learned a number of things about web frameworks, git, and many other topics
      (ask him- there will probably be a story involved!)%
    }{Daniel Allen}{Information Technology Specialist}{CSCF Web Development}

  \end{samepage}
}{}


\end{document}
